SSS

### 2020-01-01 NIME_PAPER/SSS.tex
Updates from Overleaf

\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The implementation and training of the ear guides the generation process towards a desired path.\\
\end{itemize}
Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}

\subsection{Related Work and Contradistinctions}
\label{related}
Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years. WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}. In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
\begin{enumerate}[label=\roman*]
  \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}. 
  \item Rendering at high sampling rates with little performance issues: Commonly, likely to speed up performance, the standard sampling rate in most audio generation work with neural networks appears to be under 24 khz. However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training. Therefore we can safely assume that most producers would prefer their audio samples have sampling rates of 44.1 khz or higher. \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}
  \item Neural networks are often viewed as unexplainable black box solutions. Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset. However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}. The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable. 
\end{enumerate}

\section{Implementation}
\label{impl}
\subsection{Design}

>>>>

\subsection{Methodology}
Towards our goal of generating original audio, we found the proper implementation of 2 major components to be crucial:
\begin{itemize}
    \item \textit{Virtual Synthesizer}:A flexible, deterministic, and tractable generator which can create audio. The core of our implementation made use of pippi, \footnote{https://github.com/luvsound/pippi} a fast, offline focused python DSP library with a C backend. We additionally used the scipy \cite{jones2001scipy} library a few audio effects that we found lacking in pippi. 
    \item \textit{Virtual Ear}: An ear that returns an evaluation of an audio sample; estimating the effectiveness of an audio sample's fulfillment of a producers requirements. The implementation and training of the ear guides the generation process towards a desired path. We used a labeled set of percussive and non-percussive audio files as training data to try a few different implementations of an ear, settling on a combination of a Convolutional Neural Net (CNN) model and a custom envelope detection algorithm as our "virtual drum detector ear". \\
\end{itemize}
Following the Unix Philosophy \cite{gancarz2003linux}, our components are designed with modularity and parallelizability in mind. This allows each component to be debugged, modified and improved without requiring modifications in other components; additionally, increasing the scalability and speed of experiments.
Section \ref{impl} contains further discussion of the components as well as the code that glues the project together can be found in .\\ 
While the main focus of this project is the generation of novel percussive sounds, our methodology indicates promising results with regards to creation of new presets for any virtual synth without the need for a-priori knowledge of the functions of its parameters (i.e the effect of parameter modulation on the sonic output). We also demonstrate the viability of a few lesser explored avenues for the purposes of audio synthesis and Music Information Retrieval (MIR), notably:
\begin{enumerate}[label=\roman*]
\item Heuristic search methods for the creation of new presets for virtual synthesizers. More concretely, we observed that given a virtual ear which could reliably score pieces of audio based on its resemblance to a desired category (e.g:kicks,snares,piano), we were able to rapidly search the parameters of a virtual synthesizer and create numerous parameter-sets (i.e presets) which resemble our desired category of sounds.
\item The viability of virtual synthesizers based on Digital Signal Processing (DSP) methods for fast, unsupervised creation of novel audio, discussed in more detail in section \ref{related}. \\
\end{enumerate}

\subsection{Related Work and Contradistinctions}
\label{related}
Numerous deep, neural network models have been proposed and utilized for the purpose of signal generation in recent years. WaveGans and WaveNet have been subject to significant improvements and experiments since their proposal \cite{nsynth2017} and recently, Variational AutoEncoders (VAE's) have been utilized for generation of short percussive samples \cite{aouameur2019neural,ramires2019timbfeat}. In this work however, we opt to use digital signal processing methods to create a virtual synthesizer for the generation of audio signals, as it provides several unique advantages:
\begin{enumerate}[label=\roman*]
  \item Fast, offline rendering of audio with no relience on GPU, currently not possible with state of the art models such as parallel WaveGan \cite{yamamoto2019parallel} and parallell WaveNet \cite{oord2017parallel}. 
  \item Rendering at high sampling rates with little performance issues: Performance speed being a common issue, the standard sampling rate in most audio generation work utilizing neural networks appears to be under 24 khz \cite{yamamoto2019parallel,oord2017parallel,aouameur2019neural,ramires2019timbfeat}. However, a significant number of untrained human ears can detect a change in quality of audio between sampling rates of 192 khz and the industry standard of 44.1 khz \cite{reiss2016meta}, with a dramatic increase in quality detection after training. Therefore we can safely assume that most producers would prefer their audio samples have sampling rates of 44.1 khz or higher. 
  \item Neural networks are often viewed as unexplainable black box solutions. Some models such as VAE's can learn an underlying latent space of parameters and capture the "essence" of the different labels in a dataset. However, these spaces are learned in an unsupervised manner and must be manually analysed, perhaps extensively, before they can be understood \cite{esling2018generative}. The use of a virtual synthesizer for audio generation makes our parameters readily understandable and easily modifiable. \\

\end{enumerate}
Automatic programming of virtual synthesizers has also been a topic of interest. In early 2000s, Interactive Genetic Algorithms (IGA's) were utilized for the generation of new sounds with various sound-engines \cite{johnson1999exploring,dahlstedt2001creating}. More recent work by Yee-King et al. \cite{yee2018automatic} used LSTM and genetic algorithms to find the exact parameters used to create a group of sounds. The sounds approximated were made by the same virtual synthesizer, not an external source, making the eventual replication certain, even with random search. Feature matching also appears to not be concerned with the envelope of the sounds, but rather the frequency content within arbitrary time windows. Yet another recent, impressive work by Esling et al. used a large dataset of over 10,000 presets for a commercial VST synthesizer to learn a latent parameter space which can be sampled for creation of new audio. As stated before, our work presents a rapid approximation of percussion sounds with no previous knowledge about the sonic capabilities of our virtual synthesizer.
\section{Implementation}
\label{impl}
\subsection{Design}
